Pre-Analysis Plan: Who Bends and Who Breaks? Experimental Evidence for Conditions Affecting Voters' Evaluations of Politicians Striking Compromises

### 2021-04-21 docs/pap/compromise-punishment-pap.Rmd
add updated pap

balanced <-bal.tab(Treatment ~ PreT1 + PreT2 + PreT3 + PreT4 +
                     PreT5 + PreT6 + PreT7 + PreT8 +
                     factor(F1) + F2 + factor(F9) + factor(F3) +
                     factor(F4) + factor(F5) + factor(F6) + F7 + F8,
                     Age + Education + factor(Sex_str), data = covs,
          thresholds = c(m = 0.05))[[1]]

balanced <- balanced %>%
  mutate(variable = c("Immigration (%)", "Immigration", "Defense", "Education", "Sexism",
                      "Ideology", "Poltical Efficacy", "COVID-19",
                      "Gender: Male", "Age", "Education: Middle", "Education: High",
                      "Region: West", "Region: North", "Region: East", "Region: South",
                      "Little Urban", "Moderatly Urban", "Highly Urban", 
                      "Very Highly Urban", "Migration Background", "Bij1","CDA",
                      "ChristenUnie", "D66", "Denk", "Forum for Democracy",
                      "GroenLinks", "JA21", "PvdA", "Animal Rights Party", "PVV", 
                      "SGP", "SP", "VOLT","VVD", "50Plus Party", "Employment",
                      "Income"),
         variable = factor(variable,
                           levels = c("Immigration (%)", "Immigration", "Defense",
                                      "Education", "Sexism", "Ideology", 
                                      "Poltical Efficacy","COVID-19", 
                                      "Gender: Male", "Age", "Education: Middle",
                                      "Education: High", "Region: West", "Region: North",
                                      "Region: East", "Region: South",
                                      "Little Urban", "Moderatly Urban", "Highly Urban",
                                      "Very Highly Urban", "Migration Background",
                                      "Bij1","CDA", "ChristenUnie", "D66", "Denk", 
                                      "Forum for Democracy", "GroenLinks", "JA21", 
                                      "PvdA", "Animal Rights Party", "PVV", 
                                      "SGP", "SP", "VOLT","VVD", "50Plus Party",
                                      "Employment", "Income")),
         difference = Diff.Un,2) %>%
  select(variable, difference) %>%
  ggplot(aes(x = variable, y = difference)) +
  geom_point(size = 3, colour = "gray55") +
  theme_bw() +
  labs(x="", y= "Standardized Mean Differences") +
  ggtitle("Covariate Balance") +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = 0.05, linetype = "dashed") +
  geom_hline(yintercept = -0.05, linetype = "dashed") +
  coord_flip()
```

@@

@@

depVarList <- setdiff(colnames(df), c("gender", "compromise"))
allModels <- lapply(depVarList, function(x){
  lm(formula= paste0("`", x, "` ~ gender * compromise"), 
     data= d, na.action = na.omit)})

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="gender") %>%
      select(AME, lower, upper) %>%
      mutate(y = depVarList[i])
  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="gender") %>%
      select(AME, lower, upper) %>%
      mutate(y = depVarList[i])
    m <- m %>%
      add_case(tmp)
  }
}
```

@@

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="migration") %>%
      select(AME, lower, upper) %>%
      mutate(y = depVarList[i])
  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="migration") %>%
      select(AME, lower, upper) %>%
      mutate(y = depVarList[i])
    m <- m %>%
      add_case(tmp)
  }
}
```

@@

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="intersection") %>%
      select(AME, lower, upper) %>%
      mutate(y = depVarList[i])
  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="intersection") %>%
      select(AME, lower, upper) %>%
      mutate(y = depVarList[i])
    m <- m %>%
      add_case(tmp)
  }
}
```

>>>>

balanced <-bal.tab(Treatment ~ PreT1 + PreT2 + PreT3 + PreT4 +
                     PreT5 + PreT6 + PreT7 + PreT8 +
                     factor(F1) + F2 + factor(F9) + factor(F3) +
                     factor(F4) + factor(F5) + factor(F6) + F7 + F8,
                     Age + Education + factor(Sex_str), data = covs,
          thresholds = c(m = 0.05))[[1]] 
```

@@

```{r fake-data, eval = FALSE}

df <- tibble(gender = sample(c(0,1),100, replace = T),
             compromise = sample(c(0,1),100, replace = T),
             PT1 = sample(c(0,10),100, replace = T),
             PT2 = sample(c(0,10),100, replace = T),
             PT3 = sample(c(0,10),100, replace = T),
             PT4 = sample(c(0,10),100, replace = T))
```

@@

depVarList <- setdiff(colnames(df), c("gender", "compromise"))
allModels <- lapply(depVarList, function(x){
  lm(formula= paste0("`", x, "` ~ gender * compromise"), 
     data= df, na.action = na.omit)})

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="gender") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)

  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="gender") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
    m <- m %>%
      add_case(tmp)
  }
}
```

@@

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="migration") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="migration") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
    m <- m %>%
      add_case(tmp)
  }
}
```

@@

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="intersection") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="intersection") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
    m <- m %>%
      add_case(tmp)
  }
}
```
